\documentclass[letter]{res}

\setlength{\textheight}{9.5in}
%\usepackage{fontspec}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\geometry{
 a4paper,
 total={210mm,297mm},
 left=20mm,
 right=25mm,
 top=17mm,
 bottom=17mm,
 bindingoffset=0mm
 }\usepackage{fontenc}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage[colorinlistoftodos]{todonotes}
%\setmainfont[Mapping=tex-text]{Linux Libertine O}

\begin{document}
\newif \iflong
\longtrue     % Long Version or Short one

\name{Omid Askari\\}
\address{+1 (805) 886 7101}
\address{6520 El Colegio Rd, Apt 2308, Santa Barbara, CA 93106} \href{mailto:omid55@cs.ucsb.edu}{omid55@cs.ucsb.edu}
\begin{resume}
  \noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}


% 				EDUCATION
% --------------------------------------------------------
\section{Education}
{\sl Ph.D.} - Computer Science (GPA: 4.0/4.0), UC Santa Barbara, CA\hfill Expected: September 2020\vspace{-1mm}\\
{\sl M.Sc.} - Computer Engineering (GPA: 4.0/4.0), Sharif University of Technology, Tehran\hfill February 2014\vspace{-1mm}\\
{\sl B.Sc.} - Software Engineering (GPA: 3.86/4.0), University of Isfahan, Isfahan\hfill July 2011\vspace{-1mm}


% 				AWARDS
% --------------------------------------------------------
\section{Awards} 
 \begin{itemize}
 \item Awarded 5-years fully funded scholarship and Computer Science Fellowship in UC Santa Barbara, September 2015.
 \item Ranked $1_{st}$ in Bio-Informatics HPN-DREAM Consortium Breast Cancer Network Inference Challenge (the compendium was a joint publication in Nature Methods Journal 2015), February 2014.
 \item Awarded a Full-Funded Research Scholarship of Max Planck Institute for Intelligent Systems, Tüebingen, Germany, September 2013.
 \item Ranked $1_{st}$ in B.Sc. within a class of 47, Department of Computer Engineering, July 2011.
 \item Ranked $4_{th}$ in M.Sc. within a class of 56, Department of Computer Engineering, February 2013.
 \item Awarded Fellowship of Exceptional Talents for M.Sc. Program in Sharif University of Technology, September 2011.
\end{itemize}


% 				PUBLICATIONS
% --------------------------------------------------------
\section{Publications}
\begin{enumerate}
\item M. Jalili, O. AskariSichani, Xinghuo Yu `` \textbf{Optimal pinning
controllability of complex networks: Dependence on network structure,}''
\textit{Journal of Physical Review E}, (PRE), Vol. 91, No. 1, Page 012803,
\textit{American Physical Society}, DOI:10.1103/PhysRevE.91.012803,\\
\href{http://link.aps.org/doi/10.1103/PhysRevE.91.012803}{http://link.aps.org/doi/10.1103/PhysRevE.91.012803}, 2015.
{\href{http://ce.sharif.edu/~oaskari/publications/finding_controlnodes.pdf}{\textbf{\textcolor{blue}{(link)}}}}

\item SM Hill, LM Heiser, T Cokelear, M Unger, D Carlin, Y Zhang, A Sokolov, E Paull, CK Wong, K Graim, A Bivol, H Wang, F Zhu, B Afsari, LV Danilova, AV Favorov, W Lee, D Taylor, HPN-DREAM Consortium (O. Askarisichani), GB Mills, JW Gray, M Kellen, T Norman, S Friend, EJ Fertig, Y Guan, M Song, J Stuart, H Koeppl, PT Spellman, G Stolovitzky, J Saez-Rodriguez, and S Mukherjee `` \textbf{Empirical assessment of causal network inference through a community-based effort}'',\textit{Recently accepted and to appear in \textbf{Nature Methods}}, 2015.

\item O. AskariSichani, M. Jalili, `` \textbf{Large-scale Global
Optimization through Consensus of Opinions Over Networks,}'' \textit{Journal of
the Complex Adaptive Systems Modeling}, \textit{Springer}, 1(1):11, 2013.
{\href{http://ce.sharif.edu/~oaskari/publications/large-scale_optimization.pdf}
{\textbf{\textcolor{blue}{(link)}}}}

\item O. AskariSichani, M. Jalili, `` \textbf{Influence Maximization of
Informed Agents in Social Networks,}'' \textit{Journal of Applied Mathematics
and Computation}, (AMC), Vol. 254, Pages 229-239, 3/1/2015, \textit{Elsevier},
\href{http://dx.doi.org/10.1016/j.amc.2014.12.139}{http://dx.doi.org/10.1016/j.amc.2014.12.139},%\\
%http://www.sciencedirect.com/science/article/pii/S0096300314018001
, 2015.{\href{http://ce.sharif.edu/~oaskari/publications/influence_maximization.pdf}{\textbf{\textcolor{blue}{(link)}}}}

%\item A. Gharipour, A. Yousefian, O. AskariSichani, ``\textbf{Clustering Based on Fuzzy Rules and Genetic Algorithm for $\alpha-$Reliability Decision of Asset Classification and Portfolio Selection,}'' \textit{Journal of the Asian Economic Review}, Volume 55, No. 1, Pages 47-60, 2013.{\href{http://ce.sharif.edu/~oaskari/publications/clustering_based_on_fuzzy_rules.pdf}{\textbf{\textcolor{blue}{(link)}}}}

\item A. Fatemi, K. Zamanifar, N. Nematbakhsh, O. AskariSichani, ``
\textbf{A Team-Based Organizational Model for Adaptive Multi Agent Systems,}''
in \textit{3rd International Conference on Agents and Artificial Intelligence},
\textit{ICAART} 2011, \textit{Rome}, \textit{Italy}, Volume 2, No. 297, session
10:30-11:00, 2011.
{\href{http://ce.sharif.edu/~oaskari/publications/an_adaptive_multi_agent_systems.pdf}{\textbf{\textcolor{blue}{(link)}}}}
\end{enumerate}


% 				WORK EXPERIENCES
% --------------------------------------------------------
\section{Work Experience}
\begin{itemize}
\item University of California at Santa Barbara, CA \newline
   - {\sl Research Assistant} \hfill September 2015 – Present\\
   \vspace{-4mm}
   \iflong
     \begin{itemize}
     \item Have been working under supervision of Prof. Ambuj K. Singh and Prof. Francesco 	Bullo.
     \item Collaborating with a group of researchers from different universities on a data-driven project under Multidisciplinary University Research Initiative (MURI) grant.
     \item Implementing codes with C++, Python and MATLAB to analyze real big datasets to mathematically and experimentally show the dynamics of people group formation and evolution.
     \end{itemize}
   \fi 
   
  \item Hekmat Iranian Bank, Tehran \newline
   - {\sl Full-time Business Intelligence Analyst and Senior Software Architecture} \hfill January 2015 - August 2015\\
  \vspace{-4mm}
  \iflong
    \begin{itemize}
        \item Analyzed a huge set of financial dataset
        \item Designed and managed a team of developers to build a software for computing liquidity and credit risk
        \item Implemented the software using JavaFX, WEKA, Hibernate, Persistence, Oracle Database (PL/SQL) and OLAP Data Cube technology for computing queries instantly and Data-warehouse programming
    \end{itemize}
  \fi
  
  \item Max Planck Institute (MPI) for Intelligent Systems, Empirical Inference Department, Tüebingen \newline
  - {\sl Researcher} \hfill September 2013 - January 2014\\
    \vspace{-4mm}
    \iflong
      \begin{itemize}
          \item Working on two huge datasets, Memetracker and Twitter, to mathematically model information cascades using Hawkes Process
          \item Developing Stanford Network Analysis Platform (SNAP) toolbox using C++ and learned how to execute parallel codes efficiently on Oracle Grid Engine Server
          \item Developing MATLAB codes to optimize a convex function using MATLAB CVX toolbox and Mosek.
      \end{itemize}
    \fi
  
  \item International Systems Engineering and Automation Company (IRISA) Company, Isfahan \newline
- {\sl Intern} \hfill June 2011 - September 2012\\
	\vspace{-4mm}
    \iflong
      \begin{itemize}
          \item Designed and developed one part of Oracle database in an Enterprise Resource Planning (ERP) software.
          \item Used Java Applet, Oracle Forms and PL/SQL Package Programming
          \item In a another project, developed a plug-in for an extensive Oracle infrastructure-based ERP software
          \item The software automated the query generation for mathematical formula computation using PL/SQL development and Oracle Form graphical user
      \end{itemize}
    \fi

  \item Rena Technical Services Company, Karaj \newline
- {\sl Part-time Database Consultant} \hfill July 2011 - October 2011\\
	\vspace{-4mm}

\end{itemize}

% 				PROJECTS
% --------------------------------------------------------
\section{Projects}
Adaptive Multi Agent System Toolbox \newline
  - {\sl Software Designer and Developer} \hfill 2009 – 2011\\
  \vspace{-4mm}
  \iflong
    \begin{itemize}
    \item Learned agent-oriented programming and developed a massive distributed system
    \item Simulated a robocup rescue system and implemented a toolbox for 				attribute-based team cooperation organizational modeling
    \item Used Java Agent Development Framework (JADE) for multi-thread programming, 		Swing, JFrame for graphical user interface and reporting service
    \end{itemize}
  \fi

Software for Traffic Police Law Enforcement Device \newline
   - {\sl Software Designer and Developer} \hfill 2008 – 2009\\
   \vspace{-4mm}
   \iflong
      \begin{itemize}
        \item Implemented a driver and graphical user interface for the device with C\#
        \item This project won a silver medal in IENA, International Exhibition `` Ideas-Inventions-Novelties'', November 5-8, 2009, N\"{U}RNBERG, Germany
        \item Also won another silver medal in Geneva Inventions, April 21-25, 2010, Geneva, 		Switzerland
      \end{itemize}
   \fi
   
Multi Agent System for City Traffic and Routing Simulation \newline
   - {\sl Software Designer and Developer} \hfill 2010 – 2011\\
   \vspace{-4mm}
   \iflong
     \begin{itemize}
        \item Designed and developed a parallel multi agent system software in JADE for modeling a city traffic system comprises cars, GPS and intelligent lights with an online graphical user interface exhibiting the simulation process, configuration and reporting services
      \end{itemize}
	\fi
    
Real Estate Management Software
- {\sl Software Designer and Developer} \hfill 2009\\
   \vspace{-4mm}
   \iflong
     \begin{itemize}
        \item Developed in C\# using Microsoft WPF, SQL Server 2008 Database and Entity Framework
        \item Implemented an advanced online query generator to flexibly and efficiently search in huge database of properties, lands and homes
     \end{itemize}
   \fi
   
Service-Oriented Recommender System Software with Linked-Data Technology
- {\sl Software Designer and Developer} \hfill 2010\\
   \vspace{-4mm}
   \iflong
     \begin{itemize}
        \item Developed in C\# using Microsoft WCF for service-oriented programming, Microsoft WPF
        \item Implemented a linked-data database using dotNetRDF and SPARQL
     \end{itemize}
   \fi

Time Series Forecasting in Business Intelligence Software
- {\sl Developer} \hfill 2011\\
   \vspace{-4mm}
   \iflong
     \begin{itemize}
        \item Implemented a time series forecasting software using a hybrid model of SVM, ARMA, ARIMA and ANFIS
     \end{itemize}
   \fi

% 				SKILLS
% -------------------------------------------------------- 
\section{Skills}
\textit{Academic Software Packages:}\\
{\sl Network:} \textbf{SNAP}, Matlab BGL, Gephi, Pajek, NodeXL.
{\sl Optimization:}\textbf{Matlab CVX}, \textbf{Mosek}, Gurobi.
{\sl Multi Agent Development:}\textbf{Java Agent Development Framework (JADE)}, Repast Simphony.
{\sl Representation:}\textbf{\LaTeX}, Microsoft Word, VIM, EMacs.
{\sl Parallel Task Handling Services:}{\textbf{Oracle (Sun) Grid Engine on Oracle Solaris.}}
{\sl Machine Learning and Data-mining:}{\textbf{WEKA}, Rapid Miner, Clementine.}
{\sl Linked Data \& Semantic Web:}{RDF, \textbf{SPARQL}, OWL Ontology, Jena,
\textbf{dotNetRDF}, Prot\'{e}g\'{e}.}
\vspace{-2mm}

\textit{Programming Languages:}\\
\textbf{JAVA}, C, \textbf{C++},\textbf{C\#}, \textbf{MATLAB}, Python, SQL, \textbf{PL/SQL}, TSQL, ASP.NET, PHP, JSP, Prolog, Ruby, Visual Basic, Pascal, R.
\vspace{-2mm}

\textit{Operating Systems:}\\
Windows, \textbf{Linux}, \textbf{Linux Server}, Windows Server.
\vspace{-2mm}

\textit{Development Software Packages:}\\
\textbf{Microsoft Visual Studio}, Microsoft .Net, \textbf{Windows Presentation Foundation (WPF)}, \textbf{Windows Communication Foundation (WCF)}, Microsoft Entity Framework,
Java Hibernate, Java Persistence, Java JFrame, Swing, Applet, C++ Graphical Design with \textbf{MFC}, Qt, Oracle Development Kit, Oracle Form, Android Software Programming, \textbf{Eclipse}, \textbf{Netbeans}, IntelliJ IDEA, \textbf{PyCharm}.\\
\vspace{-6mm}

\textit{Programming Paradigms:}\\
\textbf{Object-Oriented Programming}, \textbf{Agent-Oriented Programming}, \textbf{Service-Oriented Programming}.
\vspace{-6mm}

\textit{Subversion Softwares:} \textbf{Git}, TortoiseSVN.
\vspace{-2mm}
 
\textit{Database Management Systems (DBMS):}\\
\textbf{Oracle}, \textbf{Microsoft SQL(MSSQL)}, PostgreSQL, MySQL, Microsoft Access.
\vspace{-2mm}
 
%\textit{Network Skills:} CCNA certificate.
%\vspace{-2mm}


% 				ACTIVITIES
% --------------------------------------------------------
\section{Scientific Activities}
{\sl Reviewer for:}Journal of ACM Transactions on Knowledge Discovery from Data | 2014 - Present\\
{\sl Reviewer for:}Journal of Complex Networks, Oxford University Press | 2013 - Present\\
{\sl Elected President:}Scientific Society of University of Isfahan Computer Sciences Students | 2013\\
{\sl Founder and Director of:}Java Agent Development Framework (JADE) Facebook Page | 2010 - Present\\
{\sl Researcher in:}Isfahan Math House (IMH) | 2010 - 2011


% 				REFERENCES
% --------------------------------------------------------
\section{References}
\begin{itemize}
\item \textbf{Ambuj K. Singh}, \textit{Professor and Chair in Computer
Science Department, UCSB}, Main department phone: (805) 893 3236, office:
3119 Harold Frank Hall, \href{mailto:manuelgr@mpi-sws.org}{E-mail:
\textbf{ambuj@cs.ucsb.edu}}

\item \textbf{Manuel Gomez Rodriguez, PhD}, \textit{Tenure-track Research Group
Leader, Max Planck Institute for Software Systems (MPI-SWS)}, Phone: +49 (7071)
601 - 541, office: Paul-Ehrlich-Strasse, 67663 Kaiserslautern, DE, \href{mailto:manuelgr@mpi-sws.org}{E-mail: \textbf{manuelgr@mpi-sws.org}}

\item \textbf{Mahdi Jalili, PhD}, \textit{Assistant Professor, Department of Computer Engineering, Sharif University of Technology}, Phone: (+98) 21 - 66166 - 6636, \href{mailto: mjalili@sharif.edu}{E-mail: \textbf{mjalili@sharif.edu}}
\\
\end{itemize}
%----------------------------------------------------------------------------------------
\centerline{\scalebox{.75}{\textit{Modified in: \today}}}

\end{resume}
\end{document}

